"The waves danced across the vast ballroom that was the sea, occasionally bumping into each other and into the boulders. The boulders performed their job spectacularly, considering they were the guards that kept the waves from crashing against the castle, in which The Actual Ball was held."

"Man... is this even any good?" I thought to myself as I looked out the airplane window. We were now landing in Munich, Germany, the setting sun spreading its warm pink gleam over the airplane wings. I liked writing in my free time. Always tried to make it seem poetic and romantic and touching. "Tried" being the key word. Actually, writing wasn't something I was pursuing career-wise. I graduated from high school in hopes of becoming a programmer. Munich, Germany is where I'm supposed to get the degree. The school year was about to begin, I was already accepted into the university. All I had to do was settle in, get acquainted with the campus and meet my dorm roommates. I was actually quite nervous about that, I wasn't a very outgoing person, but this year's goal was to be one (or at least really really try).

\bigskip

Standing with my luggage at the line to the ticket vending machine, I was breathing in the Munich airport air. I researched before coming here, and apparently you can buy a transport card at one of those machines. Specifically, I needed the student card. I moved with the people in the line and soon enough I was face-to-face with the machine. As I tapped on the screen, I slowly came to the realization that I haven't done enough research because... they didn't sell student cards at the machines.

"Shit," I said louder than I intended.

Thankfully there was no line behind me, so I kept anxiously browsing in hopes of a student card magically appearing on the screen.

"You look like you need help," I hear a voice coming from beside me.

I turn towards it, thinking that it's probably some airport worker ready to help, but I find myself bumping into a guy in a business suit, a carry-on in his hand. I look up into his face. He looks young, around my age. Green eyes. Curly brown hair. Dimples.

"I guess I do..." I reply, "I wanted to get a student transport card but I can't seem to find it in the options."

"Ah," he smiles, "I see..."

His eyes gleam at me and he reaches his hand towards the vending machine. Taps some buttons. A message comes up saying that one should follow the instructions on the terminal and pay. Before I have time to even process what is happening, I see the stranger pull out his card. A little "ping" sound goes off as the terminal screen says "Payment accepted". He then pulls a ticket out of the machine and hands it to me.

"It'll be valid for a month. The student card is only available to order online," he says.

I stare at the ticket in my hand, then up at the stranger. This is probably a street scam. I have to make amends.

"Thank you," I say hesitantly, "How much do I owe you?"

"Nothing."

I look dumbly at him.

"I can't accept this. How much was this?"

"Don't worry about it."

I laugh nervously.

"I'm sorry, I can't accept something like this from a stranger," I say.

"Daniel Torres," he proclaims.

I stare at him even more.

"Is my name. I'm not a stranger now that you know that, right?"

"I mean, you don't know mine..."

He leaned in a little, smiling pleasantly: "You wanna tell me yours?

I considered it for a moment.

"Avril."

"Nice to meet you, Avril."

"Nice to meet you, too," I say hesitantly, "But... I still don't think I can accept this..."

He sighs, looks away and smiles.

"You know what, I \textit{would} like something in return," he says, turning his gaze back to me.

Here it comes... The street scam that my parents warned me about. He'll ask for a huge amount of money and if I don't give it to him, he'll call the police, and they'll arrest me and deport me and I will be banned from Germany and I won't get my degree and...

"Your phone number," he interrupts my thoughts.

Oh.

That was not what I expected him to say.

"What do you need my phone number for...?" I questioned cautiously.

"To call you," he answered simply.

"Um..."

"Listen, I like your voice, I'd want to hear it again," he replied.

I stared at him. If my number is all he wants, and this is not a trap or a scam, then...

I fumbled in my purse, found my phone, opened my phone number and silently showed it to him. In return, he wrote it down on his phone with a small smile.

"I'll call you," he said as he put his phone away.

Then he looked at me one more time, turned around and walked off, carry-on still in hand.